SunPy - Python for Solar Physics

### 2014-07-20 2-1-Map.tex
all single quotes to double quotes in code

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> aiamap = sunpy.map.Map('aia_file.fits')
>>> smap = aiamap.submap([-1200, -200], [-1000, -0])
>>> smap.peek(draw_grid=True)
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\end{center}
\caption{Example of the \texttt{AIAMap} specialisation of 
\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
of the map is created, and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
\label{code:aia_1}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> import matplotlib.pyplot as plt
>>> compmap = sunpy.map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
...                         composite=True)
>>> compmap.set_levels(1, range(0, 50, 5), percent=True)
>>> compmap.set_colors(1, 'Reds_r')
#Plot the result and crop
>>> ax = plt.subplot()
>>> compmap.plot()
>>> ax.axis([200, 600, -600, -200])
>>> plt.show()
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{comp_map_example}
\end{center}
\caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI data composited
on top of \textit{SDO}/AIA data. The \texttt{CompositeMap} is plotted using the integration with the \texttt{matplotlib.pyplot} interface.}
\label{code:compmap_1}
\end{listing}

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> cubemap = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
>>> cubemap.peek()
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_cube_controls}
\end{center}
\caption{Example showing the creation of a \texttt{MapCube} from a list of files. The 
resultant plot makes use of \texttt{matplotlib}'s interactive widgets to allow scrolling 
through the \texttt{MapCube}.}
\label{code:mapcube_1}
\end{listing}

>>>>

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> aiamap = sunpy.map.Map("aia_file.fits")
>>> smap = aiamap.submap([-1200, -200], [-1000, -0])
>>> smap.peek(draw_grid=True)
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\end{center}
\caption{Example of the \texttt{AIAMap} specialisation of 
\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
of the map is created, and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
\label{code:aia_1}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> import matplotlib.pyplot as plt
>>> compmap = sunpy.map.Map("aia_1600_image.fits", "RHESSI_image.fits", 
...                         composite=True)
>>> compmap.set_levels(1, range(0, 50, 5), percent=True)
>>> compmap.set_colors(1, "Reds_r")
#Plot the result and crop
>>> ax = plt.subplot()
>>> compmap.plot()
>>> ax.axis([200, 600, -600, -200])
>>> plt.show()
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{comp_map_example}
\end{center}
\caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI data composited
on top of \textit{SDO}/AIA data. The \texttt{CompositeMap} is plotted using the integration with the \texttt{matplotlib.pyplot} interface.}
\label{code:compmap_1}
\end{listing}

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> cubemap = sunpy.map.Map("aia_lev1_171a_2014_01*fits", cube=True)
>>> cubemap.peek()
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_cube_controls}
\end{center}
\caption{Example showing the creation of a \texttt{MapCube} from a list of files. The 
resultant plot makes use of \texttt{matplotlib}'s interactive widgets to allow scrolling 
through the \texttt{MapCube}.}
\label{code:mapcube_1}
\end{listing}

### 2014-07-20 2-2-Lightcurve.tex
all single quotes to double quotes in code

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import lightcurve
>>> from sunpy.time import TimeRange
>>> goes = lightcurve.GOESLightCurve.create('2011-06-07 06:00',
...                                         '2011-06-07 08:00')
>>> goes.peek()
>>> print goes.data['B_FLUX'].max()
2.55542e-05
>>> print goes.data['B_FLUX'].idxmax()
2011-06-07 06:41:26
\end{minted}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range and the output of the 
\texttt{peek()} method. The maximum flux value in the \textit{GOES} 1.0--8.0$\AA$\ channel 
is then retrieved along with the location in time of the maximum.}
\label{code:goes_lc}
\end{listing}

>>>>

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy import lightcurve
>>> from sunpy.time import TimeRange
>>> goes = lightcurve.GOESLightCurve.create(TimeRange("2011-06-07 06:00",
...                                         "2011-06-07 08:00"))
>>> goes.peek()
>>> print goes.data["B_FLUX"].max()
2.55542e-05
>>> print goes.data["B_FLUX"].idxmax()
2011-06-07 06:41:26
\end{minted}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range and the output of the 
\texttt{peek()} method. The maximum flux value in the \textit{GOES} 1.0--8.0$\AA$\ channel 
is then retrieved along with the location in time of the maximum.}
\label{code:goes_lc}
\end{listing}

### 2014-07-20 3-1-VSO.tex
all single quotes to double quotes in code

The Virtual Solar Observatory (\href{http://virtualsolar.org}{VSO}) provides a 
single, standard query interface to solar data from different archives 
around the world \citep{hill2009}.
Data products can be requested for specific instruments or missions and
can also be requested based on physical parameters of the data product such
as the wavelength range.
In addition to the VSO's primary web-based interface, a SOAP (Simple Object 
Access Protocol) service is also available.
SunPy's \texttt{vso} module provides access to the VSO via the SOAP service using the
\texttt{suds} package.

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import vso
>>> client = vso.VSOClient()
>>> tstart, tend = '2011/6/7 05:30', '2011/6/7 10:30'
>>> lasco_query = client.query(vso.attrs.Time(tstart, tend),
...                            vso.attrs.Instrument('lasco'))
>>> lasco_query.num_records()
40
>>> lasco_query.show() 
Start time           End time             Source  Instrument  Type
----------           --------             ------  ----------  ----
2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO    LASCO       CORONA
2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO    LASCO       CORONA
...
>>> pathformat = '/data/{instrument}/{detector}/{file}.fits'
>>> results = client.get(coronagraphs, path = pathformat)
\end{minted}
\caption{Example of querying a single instrument over a time range and downloading the data}
\label{code:vso_query_simple}
\end{listing}

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> condition = (vso.attrs.Detector('cor1') |
...              vso.attrs.Wave(125, 135) |
...              vso.attrs.Wave(165, 175) ) # in angstroms
>>> advanced = client.query(vso.attrs.Time(tstart, tend), condition)
>>> advanced.num_records()
4434
>>> advanced.show()
Start time           End time             Source    Instrument  Type
----------           --------             ------    ----------  ----
2011-06-07 00:00:00  2011-06-08 00:00:00  SDO       EVE         FULLDISK
...
2011-06-07 05:31:09  2011-06-07 05:31:19  PROBA2    SWAP        FULLSUN
...
2011-06-07 10:25:43  2011-06-07 10:25:45  STEREO_B  SECCHI      CORONA
2011-06-07 10:30:00  2011-06-07 10:30:01  STEREO_A  SECCHI      CORONA
...
2011-06-07 10:30:00  2011-06-07 10:30:01  SDO       AIA         FULLDISK
\end{minted}
\caption{Example of an advanced VSO query using attribute objects,
combining both data from a detector and any data that falls within two wavelength ranges,
continuing from Listing~\ref{code:vso_query_simple}.}
\label{code:vso_query_advanced}
\end{listing}

>>>>

The Virtual Solar Observatory (\href{http://virtualsolar.org}{VSO}) provides a 
single, standard query interface to solar data from different archives 
around the world \citep{hill2009}.
Data products can be requested for specific instruments or missions and
can also be requested based on physical parameters of the data product such
as the wavelength range.
In addition to the VSO's primary web-based interface, a SOAP (Simple Object 
Access Protocol) service is also available.
SunPy's \texttt{vso} module provides access to the VSO via this SOAP service using the
\texttt{suds} package.

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import vso
>>> client = vso.VSOClient()
>>> tstart, tend = "2011/6/7 05:30", "2011/6/7 10:30"
>>> lasco_query = client.query(vso.attrs.Time(tstart, tend),
...                            vso.attrs.Instrument('lasco'))
>>> lasco_query.num_records()
40
>>> lasco_query.show() 
Start time           End time             Source  Instrument  Type
----------           --------             ------  ----------  ----
2011-06-07 05:35:23  2011-06-07 05:35:48  SOHO    LASCO       CORONA
2011-06-07 05:43:09  2011-06-07 05:43:29  SOHO    LASCO       CORONA
...
>>> pathformat = "/data/{instrument}/{detector}/{file}.fits"
>>> results = client.get(coronagraphs, path = pathformat)
\end{minted}
\caption{Example of querying a single instrument over a time range and downloading the data}
\label{code:vso_query_simple}
\end{listing}

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> condition = (vso.attrs.Detector("cor1") |
...              vso.attrs.Wave(125, 135) |
...              vso.attrs.Wave(165, 175) ) # in angstroms
>>> advanced = client.query(vso.attrs.Time(tstart, tend), condition)
>>> advanced.num_records()
4434
>>> advanced.show()
Start time           End time             Source    Instrument  Type
----------           --------             ------    ----------  ----
2011-06-07 00:00:00  2011-06-08 00:00:00  SDO       EVE         FULLDISK
...
2011-06-07 05:31:09  2011-06-07 05:31:19  PROBA2    SWAP        FULLSUN
...
2011-06-07 10:25:43  2011-06-07 10:25:45  STEREO_B  SECCHI      CORONA
2011-06-07 10:30:00  2011-06-07 10:30:01  STEREO_A  SECCHI      CORONA
...
2011-06-07 10:30:00  2011-06-07 10:30:01  SDO       AIA         FULLDISK
\end{minted}
\caption{Example of an advanced VSO query using attribute objects,
combining both data from a detector and any data that falls within two wavelength ranges,
continuing from Listing~\ref{code:vso_query_simple}.}
\label{code:vso_query_advanced}
\end{listing}

### 2014-07-20 3-3-HELIO.tex
all single quotes to double quotes in code

\begin{listing}[h]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net.helio import hec
>>> hc = hec.Client()
>>> tstart, tend = '2011-06-07T06:00:00', '2011-06-07T12:00:00'
>>> event_type = 'cme'

>>>>

\begin{listing}[h]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net.helio import hec
>>> hc = hec.Client()
>>> tstart, tend = "2011-06-07T06:00:00", "2011-06-07T12:00:00"
>>> event_type = "cme"

### 2014-07-20 3-4-Helioviewer.tex
Super minor edits
all single quotes to double quotes in code

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net.helioviewer import HelioviewerClient
>>> hv = HelioviewerClient()
>>> hv.download_png('2099/01/01', 6,
...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],"+
...                 "[SOHO,LASCO,C2,white-light,1,100]",
...                 x0=0, y0=0, width=768, height=768)
\end{minted}
\begin{center}
\includegraphics[width=0.6\columnwidth]{helioviewer_overlay_example}
\end{center}
\caption{Acquisition of a PNG image composed from data from three
  separate sources.}
\label{code:hv:overlaid}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> filepath = hv.download_jp2('2012/07/05 00:30:00',
...                            observatory='SDO',
...                            instrument='HMI', detector='HMI', 
...                            measurement='continuum')
>>> sunpy.map.Map(filepath).submap([200, 550], [-400, -200]).peek()
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map}
\end{center}
\caption{Acquisition and display of a Helioviewer JPEG2000 file as a
  SunPy \texttt{Map} object. Images values are byte-scaled in the range 0-255.}
\label{code:downloadjp2}
\end{listing}

>>>>

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net.helioviewer import HelioviewerClient
>>> hv = HelioviewerClient()
>>> hv.download_png("2099/01/01", 6,
...                 "[SDO,AIA,AIA,304,1,100],[SDO,AIA,AIA,193,1,50],"+
...                 "[SOHO,LASCO,C2,white-light,1,100]",
...                 x0=0, y0=0, width=768, height=768)
\end{minted}
\begin{center}
\includegraphics[width=0.6\columnwidth]{helioviewer_overlay_example}
\end{center}
\caption{Acquisition of a PNG image composed from data from three
  separate sources.}
\label{code:hv:overlaid}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> import sunpy.map
>>> filepath = hv.download_jp2("2012/07/05 00:30:00",
...                            observatory='SDO',
...                            instrument="HMI", detector="HMI", 
...                            measurement="continuum")
>>> sunpy.map.Map(filepath).submap([200, 550], [-400, -200]).peek()
\end{minted}
\begin{center}
\includegraphics[width=0.8\columnwidth]{helioviewer_hmi_continuum_jp2_to_map}
\end{center}
\caption{Acquisition and display of a Helioviewer JPEG2000 file as a
  SunPy \texttt{Map} object. Images values are byte-scaled in the range 0--255.}
\label{code:downloadjp2}
\end{listing}

### 2014-07-20 3-5-Database.tex
all single quotes to double quotes in code

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import vso
>>> from sunpy.database import Database
>>> database = Database('sqlite:///')
>>> database.download(
...     vso.attrs.Time('2012-08-05', '2012-08-05 00:00:05'),
...     vso.attrs.Instrument('AIA'))
>>> len(database)
2
>>> from sunpy.database.tables import display_entries
>>> print display_entries(
...     database,
...     ['id', 'observation_time_start', 'wavemin', 'wavemax'])
id observation_time_start wavemin wavemax
-- ---------------------- ------- -------
1  2012-08-05 00:00:01    9.4     9.4    
2  2012-08-05 00:00:02    33.5    33.5
\end{minted}
\caption{Example usage of the \texttt{database} subpackage.}
\label{code:database}
\end{listing}

>>>>

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import vso
>>> from sunpy.database import Database
>>> database = Database("sqlite:///")
>>> database.download(
...     vso.attrs.Time("2012-08-05", "2012-08-05 00:00:05"),
...     vso.attrs.Instrument('AIA'))
>>> len(database)
2
>>> from sunpy.database.tables import display_entries
>>> print display_entries(
...     database,
...     ["id", "observation_time_start", "wavemin", "wavemax"])
id observation_time_start wavemin wavemax
-- ---------------------- ------- -------
1  2012-08-05 00:00:01    9.4     9.4    
2  2012-08-05 00:00:02    33.5    33.5
\end{minted}
\caption{Example usage of the \texttt{database} subpackage.}
\label{code:database}
\end{listing}
